%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Medium Length Graduate Curriculum Vitae
% LaTeX Template
% Version 1.1 (9/12/12)
%
% This template has been downloaded from:
% http://www.LaTeXTemplates.com
%
% Original author:
% Rensselaer Polytechnic Institute (http://www.rpi.edu/dept/arc/training/latex/resumes/)
%
% Important note:
% This template requires the res.cls file to be in the same directory as the
% .tex file. The res.cls file provides the resume style used for structuring the
% document.
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

%----------------------------------------------------------------------------------------
%	PACKAGES AND OTHER DOCUMENT CONFIGURATIONS
%----------------------------------------------------------------------------------------

\documentclass[margin, 10pt]{res} % Use the res.cls style, the font size can be changed to 11pt or 12pt here

\usepackage{helvet} % Default font is the helvetica postscript font
%\usepackage{newcent} % To change the default font to the new century schoolbook postscript font uncomment this line and comment the one above

\usepackage{lua-visual-debug}
\usepackage{enumitem}

\setlength{\textwidth}{5.1in} % Text width of the document

\begin{document}

%----------------------------------------------------------------------------------------
%	NAME AND ADDRESS SECTION
%----------------------------------------------------------------------------------------
\name{Guilherme Simas Medina Abinader}
\address{guilherme\_abinader@hotmail.com}
\address{github.com/guilhermesimas}
\address{+55 (21) 99424 6137}

%----------------------------------------------------------------------------------------

\begin{resume}

%----------------------------------------------------------------------------------------
%	OBJECTIVE SECTION
%----------------------------------------------------------------------------------------
 
\section{INTERESTS}  

Software delivery on scalable, extensible architecture. Team leadership and intrinsic motivators. Evolving, client-focused, developer-driven frameworks.

%----------------------------------------------------------------------------------------
%       Education SECTION
%----------------------------------------------------------------------------------------

\section{EDUCATION}
\employer{PUC-RJ}
\title{Bachelor's in Computer Engineering}
\dates{February 2013 - December 2017}
\begin{position}
	G.P.A: 8.3/10.0 Areas of Interest: Software Engineering, Embedded Systems.
\end{position}
\employer{Rose-Hulman Institute of Technology}
\title{Bachelor's in Computer Engineering}
\dates{August 2015 - August 2016}
\begin{position}
	G.P.A: 3.1/4.0 (Unweighted) Student in the Science Without Borders program. Also participated in a Summer research program at the Illinois Institute of Technology developing a framework for autonomous flight services.
\end{position}

%----------------------------------------------------------------------------------------
%	Technology SKILLS SECTION
%----------------------------------------------------------------------------------------

\section{TECHNOLOGY \\ SKILLS} 

{\sl Web Development:} Slim, SpringBoot Web, aiohttp. \\
{\sl Continuous Delivery:} Ansible, Terraform, Jenkins, AWS. \\
{\sl Object Oriented Design:} C++11, Java11. \\
{\sl Scripting:} Python, Nodejs, Shell, Lua. \\
{\sl Tools:} Docker, Git, Linux (Ubuntu), Atlassian Suite.
 
%----------------------------------------------------------------------------------------
%	PROFESSIONAL EXPERIENCE SECTION
%----------------------------------------------------------------------------------------
 
\section{EXPERIENCE}

	\title{Senior Software Developer}
	\employer{Zoop Technology}
	\dates{November 2018 ~ Present}
	\begin{position}%
		\vspace{-\topsep}
		\begin{itemize}[itemsep=0pt]
			\item Distributed payment processing web platform
			\item Python (aiohttp), Java (SpringBoot) and Php (Slim)
			\item Scalable architecture with dockerized applications
			\item Agile-oriented mindset and team-leadership 
		\end{itemize}
	\end{position}

	\title{Software Developer}
	\employer{PUC-Rio Software Engineering Lab}
	\dates{August, 2018 - November 2018}
	\begin{position}%
		\vspace{-\topsep}
		\begin{itemize}[itemsep=0pt]
			\item Applying new technologies towards modernization of the Oil and Gas industry
			\item Object detection using Tensorflow's deep learning toolkit
			\item CUDA kernel development and optimization
			\item Smart Contracts using Ethereum
		\end{itemize}
	\end{position}

	\title{Software Developer}
	\employer{Stone Payments}
	\dates{June, 2017 - July, 2018}
	\begin{position}%
		% TODO: Find out what is causing big break before itemize and get rid of vspace
		\vspace{-\topsep}
		% Set itemsep globally
		\begin{itemize}[itemsep=0pt]
			\item Development for C-focused portable payment terminal
			\item Point of Sale multi-device operational system development
			\item Qt framework, C++ back-end
			\item JavaScript front-end using self-developed and maintained SDK
			\item Open-source initiative
			\item SCRUM methodology 
		\end{itemize}
	\end{position}

	\title{Student}
	\employer{Google Summer of Code 2017}
	\dates{June, 2017 - August, 2017}
	\begin{position}%
		\vspace{-\topsep}
		\begin{itemize}[itemsep=0pt]
			\item Embedded Systems efficiency-focused programming
			\item Interruption oriented reactive driver development
			\item In development language Céu
			\item Contribution to Céu-Arduino development kit
			\item Open-source development initiative
		\end{itemize}
	\end{position}
\end{resume}
\end{document}
